PANCHANGE_analysis

### 2020-08-19 PANCHANGE_analysis.Rmd
plots

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(eeptools) # Needed to calculate age from birthdate
library(tidyverse)
```

@@

>>>>

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(tidyverse)
```

@@

```{r}
gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar()

gad.diff_score_prepan_retro_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
  geom_bar()

gad.diff_score_prepan_base_plot <- dat %>%
  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
  geom_bar()

```{r fig.height=5, fig.width=5}
gad.diff_score_prepan_base_plot /
  gad.diff_score_prepan_retro_plot /
  gad.diff_score_prepan_base_plot +
  plot_layout(guides = "collect", heights = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```
